Insert the article title here

### 2018-04-24 writeup/manuscript.tex
bayes correlation

Another example of differences in search strategy comes from the foraging literature \cite{kristjansson2014,johannesson2016}. Participants were asked to search through a set of items from four categories, two of which were classed as targets. In the conjunction condition (i.e. searching for red-horizontal and green-vertical line segments among red-vertical and green-horizontal distracters), most observers searched in runs of one target or another. This strategy has previously been observers in animal foraging literature \ldots. However, a sub-set of observers, termed ``super-searchers'' showed no switch cost.

@@

>>>>

Another example of differences in search strategy comes from the foraging literature \cite{kristjansson2014,johannesson2016}. Participants were asked to search through a set of items from four categories, two of which were classed as targets. In the conjunction condition (i.e. searching for red-horizontal and green-vertical line segments among red-vertical and green-horizontal distracters), most observers searched in runs of one target or another. This strategy has previously been observers in animal foraging literature \cite{dawkins1971}. However, a sub-set of observers, termed ``super-searchers'' showed no switch cost.

@@

I think he sees it as a positive thing that they tasks don't correlate, because ti suggests they capture unique variation in behaviour
glass half full approach
